### 2025-07-09 README.Rmd
add dockerfile and instructions

## How to run in your browser or download and run locally

@@

>>>>

## How to run the code in your browser

You can run the R code in this project without downloading or installing anything. Click [here](https://mybinder.org/v2/gh/benmarwick/archyjobads/main?urlpath=rstudio) to open a Binder instance with RStudio running in your web broswer. Then follow the instructions below as if you were running RStudio locally on your computer (open the `.Rproj` file in RStudio, etc.).

## How to download and run locally

@@

## How to download and run locally in a Docker container

This research compendium includes a [Dockerfile](Dockerfile) that
specifies the computational environment used to generate the results
presented in the paper. You can recreate this environment, which
includes R, RStudio and all necessary R packages, on your computer by
following these steps:

1.  Install [Docker](https://www.docker.com/get-started/) on your
    computer
2.  Download the compendium, e.g. from GitHub by clicking on the green
    `< > Code` button above, then click `Download ZIP`, then unzip on
    your computer
3.  Set your terminal working directory to the compendium, and run
    `docker build -t archyjobads .` (be sure to include the period) to build 
    the container on your computer, it will take a few minutes and require 
    a fast internet connection.
4.  Run in your terminal
    `docker run --rm -it -e ROOT=TRUE -e PASSWORD=rstudio -dp 8787:8787 archyjobads`
    to start the container on your computer
5.  Go to <http://localhost:8787/> with your browser and enter `rstudio`
    in both fields to start RStudio in your browser, running in the
    Docker container with all the required depedencies installed
6.  In RStudio, run
    `rstudioapi::openProject("/home/rstudio/archyjobads")`
    to open the compendium’s project. This project uses
    [`renv`](https://rstudio.github.io/renv/) to document and manage
    dependencies, this will be activated when the project is first
    opened in RStudio.
7.  Run
    `rmarkdown::render("analysis/paper/article.qmd", output_dir='/tmp')`
    to render the Quarto document that is the manuscript submitted for
    publication
8.  After the code has executed, view the rendered output document by
    running `browseURL("/tmp/article.docx")`
9.  When finished, to delete the Docker container from your computer,
    run this in the terminal on your desktop:
    `docker ps -aq | xargs docker stop | xargs docker rm`
